\section{Simulated samples}
\label{sec:simulatedsamples}

The bulk graviton model 
% the Randall-Sundrum graviton model (RS1) %%% Thiago: is this actually used?
and the HVT model (\PWpr{}) are used as benchmark signal processes.
In these models, the vector gauge bosons are produced with a longitudinal polarisation ($\mathrm{V}_{\mathrm{L}}$) in more than 99\% of the cases.
% while in the RS1 model, their polarisation is transverse ($\mathrm{V}_{\mathrm{T}}$) in more than 90\% of the cases.
For the HVT model, a scenario (model B) is chosen where the \PWpr{} predominantly couple to bosons; that scenario is the most representative of a composite Higgs model.
Different mass hypotheses are considered for the posited resonance, in the range 800 to 4500\GeV.
Simulated signal samples are generated with the leading-order (LO) mode of \amcatnlo{} v5.2.2.2~\cite{Alwall:2014hca} with a relative resonance width of 0.1\%.
We restrict the analysis to scenarios where the natural width of the resonance is sufficiently small to be neglected when compared to the detector resolution.
This makes our modelling of the detector effects on the signal shape independent of the actual model used for generating the events.

Monte Carlo simulated samples (MC) of the SM background processes are used to optimise the analyses.
The W+jets and Z+jets SM processes are simulated with \amcatnlo{},
while \ttbar and single top quark events are generated with \POWHEG v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd,Alioli:2009je,Re:2010bp,Alioli:2011as}
and \amcatnlo{}. %%% Thiago: is this true?
Diboson (WW, WZ, and ZZ) processes are produced with \PYTHIA v8.205 \cite{Sjostrand:2006za,Sjostrand:2007gs}. 
The parton showering and hadronisation are performed with \PYTHIA using the CUETP8M1 tune~\cite{Skands:2014pea,CMS-PAS-GEN-14-001}.
The NNPDF 3.0~\cite{Ball:2011mu} parton distribution functions (PDF) are used in all generated samples. 
All generated samples are processed through a \GEANTfour-based~\cite{Agostinelli:2002hh} simulation of the CMS detector. 
The simulated background samples are normalised using inclusive cross sections calculated at next-to-leading order (NLO), or
next-to-next-to-leading order (NNLO) where available, calculated with \textsc{mcfm} v6.6 \cite{MCFM:VJets,MCFM:VV,Campbell:2012uf,MCFM:SingleTop} and \textsc{fewz} v3.1 \cite{FEWZ3}.

Supplementary minimum bias interactions are added to the generated events in order to match the additional particle production observed in data from the large number of proton-proton interactions occurring per LHC bunch crossing (pileup). The simulated samples are corrected for observed differences between data and simulation in the efficiencies of lepton trigger, lepton identification/isolation, and selection criteria identifying jets originating from hadronisation of b quarks (b jets).
