
\MADGRAPH~v5.2~\cite{Alwall:2014hca} is used to generate generic high-mass resonances:
a model with a $\Zprime$ boson with
the same left- and right-handed coupling to fermions as the SM $Z$ boson,
and masses between $500\GeV$ and $4\TeV$, was implemented.
Higher-order parton radiations are calculated 
for up to three extra partons at tree-level.
The $\Zprime$ boson is set to decay into
a $\ttbar$ pair in all generated events.
The width of the resonances is set to
both $1\%$ and $10\%$ of the $\Zprime$ boson mass.
For the $\Zprime$ boson mass points of $1$, $2$, $3$, and $4\TeV$,
additional samples with a resonance width of $30\%$ have been generated.
The parton showering is modeled with \PYTHIA~8.2~\cite{Sjostrand:2006za,Sjostrand:2014zea},
the MLM algorithm~\cite{mlm} is used for the matching. 

\PYTHIA~8.2 is used to generate a
Kaluza--Klein excitation of a gluon
which also results in a $\ttbar$ resonance production. 
Kaluza--Klein gluon excitations are generated with resonance masses between $500\GeV$ and $4\TeV$.
The branching ratio of the resonance state into top quark pairs is about $94\%$,
$6\%$ of the generated KK gluons decay into light quarks (mostly b quark pairs).
The branching ratios depend on the specific Kaluza--Klein coupling parameters. 
For the studied model, the respective \PYTHIA parameters are set to
the default values in \PYTHIA,
except the coupling of the Kaluza--Klein gluon
to right-handed top quarks which has been set to a value of 5.

Top quark pair events, produced via the strong interaction,
and electroweak production of single top quarks in the tW channel
are generated with the next-to-leading-order generator
\POWHEG~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd,Frixione:2007nw,Re:2010bp}.
The s- and t-channel processes of single top quark production
are generated with \aMCATNLO~\cite{Alwall:2014hca}.
All samples are interfaced to \PYTHIA~8.2 for the showering. 

$\W$ and $\Z$ boson productions in association with jets have been produced with \MADGRAPH~v5.2.
The MLM matching scheme is used to interface them with the shower generated with \PYTHIA.
Up to four additional partons in the matrix element are included.
%The $\W$ and $\Z$ boson samples are binned in $\HT$, where $\HT$ is the summed momentum of all final state partons in the matrix element.
%Alternative samples for $\W$ and $\Z$ boson production have been processed with aMC@NLO.
%These samples are inclusive and not binned in $\HT$. 
%The matching to the parton shower with \PYTHIA is performed with the FXFX merging algorithm~\cite{Frederix:2012ps}.
%Up to two additional jets are included in the matrix element.
Diboson processes ($\W\W$, $\W\Z$ and $\Z\Z$) are generated
with \PYTHIA for matrix element and showering.

All events were generated at the center of mass 
energy of $13\TeV$ and use the NNPDF~3.0 PDF sets~\cite{Ball:2014uwa}.
In the parton shower generated with \PYTHIA, the underlying event tune CUETP8M1 has been used.
All simulated samples include the simulation of additional inelastic proton-proton interactions
within the same bunch crossing (``in-time pileup'') and the simulation
of additional contribution in the signal readout from the previous and next bunch crossing (``out-of-time pileup'')
which are assumed to be $25\,\text{ns}$ apart from the main bunch crossing.
%The resolution and efficiencies for reconstructed objects are corrected
%to match the ones measured in data.
